---
title: "BUENAFE FA2"
output:
pdf_document: default
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE}
library(ggplot2)

```


1. Use R to illustrate that the probability of getting:

(a) a head is 0.5 if a fair coin is tossed repeatedly;
```{r COIN}
trials=1000

head_vector=numeric(trials)

#simulating trials
for (i in 1:trials) {
  # (a) Probability of getting a head when a fair coin is tossed repeatedly:
  coin_tosses=sample(c("H", "T"), i, replace = TRUE)
  head_vector[i]=mean(coin_tosses == "H")
}

dframe1=data.frame(Trials = 1:trials,
                 Prob_Head = head_vector)

ggplot(dframe1, aes(x = Trials)) +
geom_line(aes(y = Prob_Head, color = "Head")) +
labs(title = "Probability of getting a head on a coin toss",
x = "Trials",
y = "Probability",
color = "Event",
caption = "Simulated with increasing number of trials") +
scale_color_manual(values = c("steelblue")) +
theme_minimal()

```
(b) a red card is 0.5 if cards are drawn repeatedly with replacement from awell-shuffled deck;
```{r CARD} 
trials=1000

Red_vector=numeric(trials)

#simulating trials
for (i in 1:trials) {
  # (a) Probability of getting a head when a fair coin is tossed repeatedly:
  card_draws=sample(c("Black", "Red"), i, replace = TRUE)
  Red_vector[i]=mean( card_draws == "Red")
}

dframe2=data.frame(Trials = 1:trials,
                 Prob_Red = Red_vector)

ggplot(dframe2, aes(x = Trials)) +
geom_line(aes(y = Prob_Red, color = "Head")) +
labs(title = "Probability of drawing Red cards",
x = "Trials",
y = "Probability",
color = "Event",
caption = "Simulated with increasing number of trials") +
scale_color_manual(values = c("red")) +
theme_minimal()

```


(c) an even number is 0.5 if a fair die is rolled repeatedly.
```{r DICE}
trials=1000

even_vector=numeric(trials)

#simulating trials
for (i in 1:trials) {
  # (a) Probability of getting a head when a fair coin is tossed repeatedly:
  dice_roll=sample(c("Even", "Odd"), i, replace = TRUE)
  even_vector[i]=mean( dice_roll == "Even")
}

dframe3=data.frame(Trials = 1:trials,
                 dice_roll = even_vector)

ggplot(dframe3, aes(x = Trials)) +
geom_line(aes(y = dice_roll, color = "Even numbers")) +
labs(title = "Probability of getting an even number",
x = "Trials",
y = "Probability",
color = "Event",
caption = "Simulated with increasing number of trials") +
scale_color_manual(values = c("green")) +
theme_minimal()

```

3. 4. Amy and Jane are gambling together. A fair coin is tossed repeatedly. Each time a head comes up, Amy wins two euro from Jane, and each time a tail comes up, Amy loses two euro to Jane. Use R to simulate this game 100 times, and estimate:

(a) the number of times that Amy is ahead in these 100 tosses;

```{r 4a}
numtrial= 100

A_ahead= 0

for (i in 1:numtrial){
  coin_toss=sample(0:1,1, replace=T)

if (coin_toss==1){
  A_ahead[i]=1
}else {
  A_ahead[i]=-1
}
}
a_total=sum(A_ahead)
print(paste("The total number that Amy was ahead in ",numtrial," trials is ",a_total))
```
 
(b) how much Amy has won or lost after 100 tosses.
```{r 4b}
numtrial= 100

A_winnings= numeric(numtrial)
J_winnings= numeric(numtrial)


for (i in 1:numtrial){
  coin_toss=sample(c("H","T"),1, replace=T)

if (coin_toss=="H"){
  A_winnings[i]=2
  J_winnings[i]=-2
}else {
  A_winnings[i]=-2
  J_winnings[i]=2
}
}
Amy_Winnings = sum(A_winnings)
Jane_Winnings = sum(J_winnings)

Amy_Winnings
Jane_Winnings
```
Amy won a total of 8 euros on their bet
