---
title: "BUENAFE FA1"
output:
  pdf_document: default
  html_document:
    df_print: paged
date: "2024-02-01"
---

```{r setup, include=FALSE}
install.packages("e1071", repos = "https://cran.r-project.org")
install.packages('ggplot2')

library(e1071)
library(ggplot2)

Result= read.csv('C:/Users/edtech4/Documents/BUENR/data.csv')
Result
```

##Write the skewness program, and use it to calculate the skewness coefficient of
##the four examination subjects in results.txt (results.csv). What can you say about
##these data?

```{r arch1 skew}
skewarch1<- skewness(Result$arch1, na.rm=TRUE)
cat("Skewness", skewarch1, "\n")

#pearson
skewarch1= (3*(mean(Result$arch1,na.rm=TRUE)-median(Result$arch1,na.rm=TRUE)))/sd(Result$arch1,na.rm=TRUE)
print(skewarch1)

ggplot(Result, aes(x=arch1), na.rm=TRUE)+geom_density(fill="orange", color="black", alpha=1)+
  labs(title="Skewness of Arch 1", x="Score",y="Frequency")+ theme_minimal()
```

## prog1

```{r prog1 skew}
skewprog1<- skewness(Result$prog1, na.rm=TRUE)
cat("Skewness", skewprog1, "\n")

#pearson
skewprog1= (3*(mean(Result$prog1,na.rm=TRUE)-median(Result$prog1,na.rm=TRUE)))/sd(Result$prog1,na.rm=TRUE)
print(skewprog1)

ggplot(Result, aes(x=prog1), na.rm=TRUE)+geom_density( fill="orange", color="black", alpha=1)+
  labs(title="Skewness of Prog1", x="Score",y="Frequency")+ theme_minimal()
```

```{r arch2 skew}
skewarch2<- skewness(Result$arch2, na.rm=TRUE)
cat("Skewness", skewarch2, "\n")

#pearson
skewarch2= (3*(mean(Result$arch2,na.rm=TRUE)-median(Result$arch2,na.rm=TRUE)))/sd(Result$arch2,na.rm=TRUE)
print(skewarch2)

ggplot(Result, aes(x=arch2), na.rm=TRUE)+geom_density(fill="orange", color="black", alpha=1)+
  labs(title="Skewness of Arch 2", x="Score",y="Frequency")+ theme_minimal()
```
```{r prog2 skew}
skewprog2<- skewness(Result$prog2, na.rm=TRUE)
cat("Skewness", skewprog2, "\n")

#pearson
skewprog2= (3*(mean(Result$prog2,na.rm=TRUE)-median(Result$prog2,na.rm=TRUE)))/sd(Result$prog2,na.rm=TRUE)
skewprog2

#graph
ggplot(Result, aes(x=prog2), na.rm=TRUE)+geom_density( fill="orange", color="black", alpha=1)+
  labs(title="Skewness of Prog2", x="Score",y="Frequency")+ theme_minimal()
```

#Pearson’s formula to isn’t accurate and precise. Data shows that there’s an instance that
#the approximation formula isn’t close to the true value of skewness.


#2. For the class of 50 students of computing detailed in Exercise 1.1, use R to

```{r No.2}
Result2= read.csv('C:/Users/edtech4/Documents/BUENR/fa1_no2.csv')
Result2
```

#STEM-AND-LEAF DISPLAY
```{r Stem-and-leaf display}
####male score
stem(Result2$mscore)
ggplot(Result2, aes(x=mscore), na.rm=TRUE)+geom_histogram(binwidth =2, fill="orange", color="black", alpha=1)+
  labs(title="Scores of Male Students", x="Score",y="Frequency")+ theme_minimal()
```

```{r Stem-and-leaf display}
#female score
stem(Result2$fscore)
ggplot(Result2, aes(x=fscore), na.rm=TRUE)+geom_histogram(binwidth =2, fill="orange", color="black", alpha=1)+
  labs(title="Scores of Female Students", x="Score",y="Frequency")+ theme_minimal()
```
#Stem-and-leaf display provides an easier and precise visualization of data that
#goes beyond just considering the frequency which is what histogram can’t offer.


#construct a box-plot for each gender and discuss the findings

```{r}
ggplot(Result2, aes(x = 1, y = mscore)) +
  geom_boxplot(fill = "skyblue", color = "black", alpha = 0.7) +
  geom_boxplot(aes(x = 2, y = fscore), fill = "lightgreen", color = "black", alpha = 0.7) +
  labs(title = "        Comparison of scores between male and female students", x = "Students", y = "Values") +
  theme_minimal() +
  scale_x_continuous(breaks = c(1, 2), labels = c("Male students", "Female Students"))
```

#Data shows that the scores of female students are higher compared to the scores of
#most male students. It also shows how only one male student scored higher (86)
#than the other male students hence the dot separated from the box-plot
