---
title: "FA3 BUENAFE"
output: html_document
date: "2024-02-23"
---

```{r setup, include=FALSE}
library(ggplot2)
```

2.  A binary communication channel carries data as one of two sets of signals denoted by 0 and 1. Owing to noise, a transmitted 0 is sometimes received as a 1, and a transmitted 1 is sometimes received as a 0. For a given channel, it can be assumed that a transmitted 0 is correctly received with probability 0.95, and a transmitted 1 is correctly received with probability 0.75. Also, 70% of all messages are transmitted as a 0. If a signal is sent, determine the probability that:

(a) a 1 was received;

```{r 2}
transmitted_0=0.7
transmitted_1=1-transmitted_0
receiving_1=0.75
not_receiving_1=0.25
receiving_0=0.95

#a 1 was received;
Pr_1= (transmitted_0*(1-receiving_0))+receiving_1*transmitted_1
Pr_1

#a 1 was transmitted given than a 1 was received. 
Pg1_1r <- (transmitted_1 * receiving_1) / Pr_1
Pg1_1r

dframe= data.frame(
  Event= c("A 1 was received", "A 1 was transmitted given that a 1 was received"),
  Probability = c(Pr_1, Pg1_1r)
)

# Create a bar plot using ggplot
dframe <- data.frame(
  Events = c("Probability that a 1 was received", "Probability that a 1 was transmitted given that a 1 was received"),
  Probabilities = c(Pr_1, Pg1_1r)
)

ggplot(dframe, aes(x = Events, y = Probabilities, fill = Events))+
  geom_bar(stat = "identity") +
  labs(title = "Probabilities",
       y = "Probability", ) +
  theme_minimal()

```

7.  There are three employees working at an IT company: Jane, Amy, and Ava, doing 10%, 30%, and 60% of the programming, respectively. 8% of Jane’s work, 5% of Amy’s work, and just 1% of Ava‘s work is in error. What is the overall percentage of error? If a program is found with an error, who is the most likely person to have written it? 

```{r 7}
Jane=0.1
Amy=0.3
Ava=0.6
ErrorJane=0.08
ErrorAmy=0.05
ErrorAva=0.01

Total_error=Jane*ErrorJane+Amy*ErrorAmy+Ava*ErrorAva

print("Total percentage of error:")
print(Total_error*100)

Prob_JaneError=(Jane*ErrorJane)/Total_error
Prob_AmyError=(Amy*ErrorAmy)/Total_error
Prob_AvaError=(Ava*ErrorAva)/Total_error

Prob_JaneError
Prob_AmyError
Prob_AvaError

dframe2 <- data.frame(
  Events = c("Jane Probability of Error", "Amy Probability of Error","Ava Probability of Error"),
  Probabilities = c(Prob_JaneError, Prob_AmyError, Prob_AvaError )
)

ggplot(dframe2, aes(x = Events, y = Probabilities, fill = Events))+
  geom_bar(stat = "identity") +
  labs(title = "Probabilities",
       y = "Probability", ) +
  theme_minimal()
```
AMY IS THE ONE WHO IS MOST LIKELY TO HAVE WRITTEN THE ERROR WITH A PROBABILITY OF 51.7%

