---
title: "FA7"
output:
  word_document: default
  html_document: default
  pdf_document: default
date: "2024-02-29"
---

1. In Example 16.3 with ðœ† = 4 per minute, use R to obtain:
(a) P(T â‰¤ 0.25) = P(time between submissions is at most 15 seconds);
(b) P(T > 0.5) = P(time between submissions is greater than 30 seconds); (c) P(0.25 < T < 1) = P(time between submissions is between 15 seconds
and 1 minute).

```{r setup}
library(ggplot2)
lambda= 4
```


```{r prob 1}
interval_a=0.25
interval_b=0.5
interval_c_start=0.25
interval_c_end= 1

prob_a= ppois(interval_a, lambda)
prob_b= 1- ppois(interval_b, lambda)
prob_c= ppois(interval_c_end, lambda) - ppois(interval_c_start, lambda)

cat("The probability that the time between submissions is at most 15 seconds is:",prob_a*100,"%\n\n")
cat("The probability that the time between submissions is greater than 30 seconds:",prob_b*100,"%\n\n")
cat("The probability that the time between submissions is greater than 30 seconds:",prob_c*100,"%\n\n")

intervals= c("Interval A(at most 15 seconds)", "Interval B(greater than 30 seconds)", "Interval C(between 15 seconds
and 1 minute)")
probabilities= c(prob_a, prob_b, prob_c)

data= data.frame(Intervals=intervals, Probability=probabilities)


```

The average rate of job submissions in a computer center is 2 per minute. If it can be assumed that the number of submissions per minute has a Poisson distribution, calculate the probability that:
(a) more than two jobs will arrive in a minute;

```{r prob3 a}
lambda3=2
cat("The probability that more than two jobs will arrive in a minute is:",ppois(1,lambda3)*100,"%\n\n")
```
(b) at least 30 seconds will elapse between any two jobs;
```{r prob3 b}
cat("The probability that at least 30 seconds will elapse between any two jobs is:",sum(dpois(0:1,lambda3))*100,"%\n\n")
```
(c) less than 30 seconds will elapse between jobs;
```{r prob3 C}
cat("The probability that less than 30 seconds will elapse between jobs is:",(dpois(0.5,lambda3)-dpois(0,lambda3))*100,"%\n\n")
```
(d) a job will arrive in the next 30 seconds, if no jobs have arrived in the last
30 seconds
```{r prob3 D}
cat("The probability that a job will arrive in the next 30 seconds, if no jobs have arrived in the last
30 seconds is:",ppois(1,lambda3)-ppois(.5,lambda3)*100,"%\n\n")
```

A website receives an average of 15 visits per hour, which arrive following a Poisson distribution.
(a) Calculate the probability that at least 10 minutes will elapse without a visit.
```{r prob7 A}
lambda7=15
lambmin=15/60
cat("The probability that at least 10 minutes will elapse without a visit:",pexp(10,lambmin)*100,"%\n\n")
```
(b) Whatistheprobabilitythatinanyhour,therewillbelessthaneightvisits?
```{r prob7 B}
lambda7=15
lambmin=15/60
cat("The probability that in any hour,there will be less than eight visits is:",ppois(7,lambda7)*100,"%\n\n")
```
(c) Suppose that 15 minutes have elapsed since the last visit,what is the probability that a visit will occur in the next 15 minutes.
```{r prob7 C}
lambda7=15
lambmin=15/60
cat("The probability that in any hour,there will be less than eight visits is:",pexp(15,lambmin)*100,"%\n\n")
```
(d) Calculate the top quartile, and explain what it means.
```{r prob7 D}
lambda7=15
lambmin=15/60
cat("The top quartile is:",qexp(0.75,lambmin),"\n\n")
```
it means that there's 75% chance that a user will visit the website in the next 5.45 minutes