---
title: "FA8_BUENAFE"
output:
  html_document: default
  word_document: default
  pdf_document: default
date: "2024-04-18"
---
An analogue signal received at a detector, measured in microvolts, is normally distributed with mean of 200 and variance of 256.
```{r 1 }
mean=200
variance=256
sdv=sqrt(variance)
```

(a) What is the probability that the signal will exceed 224 ğœ‡V?
```{r 1a}
exc224= 1 - pnorm(224,mean,sdv)
cat("The probability that the signal will exceed 224 ğœ‡V is",exc224*100,"%")
```
(b) What is the probability that it will be between 186 and 224 ğœ‡V?
```{r 1b}
exc186_224= pnorm(224,mean,sdv) -pnorm(186,mean,sdv)
cat("The probability that the signal will be between 186 and 224 ğœ‡V is",exc186_224*100,"%")
```
(c) What is the micro voltage below which 25% of the signals will be?
```{r c}
v25p= qnorm(0.25,mean,sdv)
cat("The micro voltage below 25% of the signals will be ",v25p,"ğœ‡V")
```
(d) What is the probability that the signal will be less than 240 ğœ‡V, given that it is larger than 210 ğœ‡V?
```{r 1d}
exc210_240= (pnorm(240,mean,sdv) -pnorm(210,mean,sdv))/(1-pnorm(210,mean,sdv))
cat("The probability that the signal will be less than 240 ğœ‡V, given that it is larger than 210 ğœ‡V is",exc210_240*100,"%")
```
(e) Estimate the interquartile range.
```{r 1e}
intq= qnorm(0.75,mean,sdv)-qnorm(0.25,mean,sdv)
cat("The interquartile range is",intq,"ğœ‡V")
```
(f) What is the probability that the signal will be less than 220 ğœ‡V, given that
it is larger than 210 ğœ‡V?
```{r 1f}
exc210_220= (pnorm(220,mean,sdv) -pnorm(210,mean,sdv))/(1-pnorm(210,mean,sdv))
cat("The probability that the signal will be less than 220 ğœ‡V, given that it is larger than 210 ğœ‡V is",exc210_220*100,"%")
```

(g) If we know that a received signal is greater that 200 ğœ‡V, what is the prob-
ability that is in fact greater than 220 ğœ‡V?
```{r 1g}
exc200_220= (1 - pnorm(220,mean,sdv))/(1-pnorm(200,mean,sdv))
cat("The probability that a received signal is greater that 200 ğœ‡V is",exc200_220*100,"%")
```

2. A manufacturer of a particular type of computer system is interested in improving its customer support services. As a first step, its marketing department has been charged with the responsibility of summarizing the extent of customer problems in terms of system failures. Over a period of six months, customers were surveyed and the amount of downtime (in minutes) due to system failures they had experienced during the previous month was collected. The average downtime was found to be 25 minutes and a variance of 144. If it can be assumed that downtime is normally distributed:
```{r 2}
avg_dt=25
variance2= 144
sdv2=sqrt(variance2)
```
(a) obtain bounds which will include 95% of the downtime of all the customers;
```{r 2a}
upb95=qnorm(0.975, avg_dt , sdv2)
lwb95=qnorm(0.025, avg_dt , sdv2)

cat("The bounds that include 95% of the downtime of all customers is",lwb95," and ",upb95 )
```

(b) obtain the bound above which 10% of the downtime is included.
```{r 2b}
upb10=qnorm(0.90, avg_dt, sdv2)
cat("The upper bound that includes 95% of the downtime of all the customers is",upb10)
```